Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-19 paper/paper.qmd
update paper.qmd

The data was cleaned and analyzed using the 'R' programming language[@citeR] and the following packages were used: 'tidyverse' [@tidyverse], 'janitor' [@janitor],`dplyr` [@Dplyr], `ggplot2` [@citeggplot2], `here` [@herePackage], `kableExtra` [@citekableExtra], `knitr` [@knitr], `modelsummary` [@model], `readr` [@readr], `tibble` [@tibblePackage] and 'arrow' [@arrow]

@@

# Discussion

## Growth in Female Literacy Rate in South Asia

As analyzed in @fig-1,  the female literacy rate in South Asia is on the rise over the last two decades with a literacy rate of approximately 44.9 percent in the year 2000 to approximately 64.6 percent in 2020. This upward trend is not confined to the past two decades only. South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_Literacy].

## Declining Fertility Rate (total births per woman)in South Asia

As analyzed in @fig-2,  the fertility rate in South Asia is on the decline over the last two decades with a fertility rate of approximately 3.57 births per woman in the year 2000 to approximately 2.26 births per woman in 2020. This downward trend is not confined to the past two decades only. Fertility rate in South Asia has long been on a decline. The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_Fertility].

## Impact of Female Literacy Rate on Fertility Rate

>>>>

The data was cleaned and analyzed using the `R` programming language[@citeR] and the following packages were used: `tidyverse` [@tidyverse], `janitor` [@janitor],`dplyr` [@Dplyr], `ggplot2` [@citeggplot2], `here` [@herePackage], `kableExtra` [@citekableExtra], `knitr` [@knitr], `modelsummary` [@model], `readr` [@readr], `tibble` [@tibblePackage] and `arrow` [@arrow]

@@
